---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---

First we install the required packages.
```{r message=FALSE, warning=FALSE, echo=FALSE}
# Install packages
#install.packages(c("RPostgreSQL"), quiet = TRUE)
```

Second we load libraries we need
```{r message=FALSE}
require("RPostgreSQL")
require("knitr")
require("ggplot2")
require(psych)
require(dplyr)
```

Check if we can connect to the db and if sessions table does exist (some sort of validation!).
```{r}
# loads the PostgreSQL driver
drv <- dbDriver("PostgreSQL")
# creates a connection to the postgres database
# note that "connection" will be used later in each connection to the database
connection <- dbConnect(drv, dbname = "postgres", password = "1way.Street",
                 host = "localhost", port = 5432,
                 user = "postgres")



# check for the cartable
dbExistsTable(connection, "session")
# TRUE
```

Get list of sessions and their lengths both in terms `length(sessions`  of time and number of measurements.

```{python}
print 5
```


```{r}
query <- "SELECT id,e1.start,e1.finish-e1.start as duration,e2.count_values
FROM session AS e1
LEFT JOIN LATERAL (
    SELECT COUNT(*) AS count_values
    FROM datavr
    WHERE e1.id=datavr.idsession)
    AS e2
ON TRUE;"
sessions <- dbGetQuery(connection, query)
```


```{r kable}
kable(sessions)
```

```{r get-session-data}
session_id = 390
query <- "SELECT datavr.*,datasteering.steering,datasteering.accelerator,datasteering.slider1 AS brake FROM
datasteering 
JOIN datavr ON datasteering.time=datavr.time AND datasteering.idsession=datavr.idsession
WHERE datasteering.idsession=$1;"
session_data <- dbGetQuery(connection, query,c(session_id))
```

```{r}
summary(session_data)
```

```{r}
session_data$steering[order(session_data$steering)[1:5]]
order(session_data$steering)[1:5]
```

```{r}
#session_data_filtered <- session_data %>%
#  filter(steering>-1001,accelerator>-1001,slider1>-1001)

session_data_filtered <- session_data %>%
  filter(steering>-1001,accelerator>-1001)

session_data_filtered$longitudinal = (-session_data_filtered$accelerator+1000)-(-session_data_filtered$brake+1000)
```

```{r}
summary(session_data_filtered)
```


Plot histogram of Gas pedal
```{r}
ggplot(data=session_data_filtered, aes(x="k", y=session_data_filtered$steering)) + geom_boxplot()
```


Plot histogram of Brake pedal
```{r}
ggplot(data=session_data_filtered, aes(session_data_filtered$brake)) + geom_density()
```

Plot histogram of Steering
```{r}
ggplot(data=session_data_filtered, aes(session_data_filtered$steering)) + geom_density()
```

```{r}
ggplot(session_data_filtered, aes(x=steering, y=-accelerator)) +
    geom_point(shape=1)      # Use hollow circles
```


```{r}
ggplot(session_data_filtered, aes(x=steering, y=brake)) +
    geom_point(shape=1)      # Use hollow circles
```


```{r}
ggplot(session_data_filtered, aes(x=steering, y=longitudinal)) +
    geom_point(shape=1)      # Use hollow circles
```

Heatmap of X-Y of headset
```{r}
k <- with(session_data_filtered,MASS::kde2d(-rotationy,rotationx,n=50,lims=c(-0.2, 0.6, -0.1, 0.3)))
filled.contour(k,color = terrain.colors)
```

```{r}
m <- ggplot(session_data_filtered, aes(x = -rotationy, y = rotationx)) +
 geom_point()
m + geom_density_2d()
```






```{r}
m <- ggplot(session_data_filtered, aes(x = -rotationy, y = rotationx))
m + stat_density_2d(geom = "raster", aes(fill = ..density..), contour = FALSE) +
  scale_fill_gradientn(colours = terrain.colors(10))
```





```{r}
library(pspline)
t1 = predict(sm.spline(session_data_filtered$time, session_data_filtered$steering), session_data_filtered$time, 1)
```

```{r get-position-data}
session_id = 392
query <- 'SELECT * FROM public."WorldSpeed" WHERE idSession=$1;'
postion_data <- dbGetQuery(connection, query,c(session_id))
```

```{r}
summary(postion_data)
```

```{r}
ggplot(postion_data, aes(x=posx, y=posy, color=speed)) +
      geom_point(shape=16, size = 0.75)  + scale_x_continuous(limits = c(-750, 750)) + scale_color_gradient(low="blue", high="red")
ggsave("positionAndSpeed.png", width = 7, height = 5)
```

```{r}
ggplot(postion_data, aes(x=posx, y=posy, color=speed)) +
      geom_path(shape=16, size = 1.5)  + scale_x_continuous(limits = c(-750, 750)) + scale_color_gradient(low="blue", high="red")
```


```{r get-session-data2}
normalizar <- function(x){
  returnValue(x/65535)
}

session_id = 392
query <- "SELECT datavr.*,datasteering.steering,datasteering.accelerator,datasteering.brake FROM
datasteering 
JOIN datavr ON datasteering.time=datavr.time AND datasteering.idsession=datavr.idsession
WHERE datasteering.idsession=$1;"
session_data2 <- dbGetQuery(connection, query,c(session_id))

data_scale <- session_data2 %>% mutate_each_(funs(scale(.) %>% as.vector), 
                             vars=c("positionx","positiony", "positionz", "rotationx", "rotationy", "rotationz"))
data_scale2 <- session_data2 %>% mutate_each_(funs(normalizar(.) %>% as.vector), 
                             vars=c("accelerator","steering", "brake"))
#apply(session_data2[,c('accelerator','steering', 'brake')], 1, function(x) x/64555 )
```

```{r}
summary(data_scale)
quantile(data_scale$positionx, 0.25)
```


```{r}
ggplot(data=data_scale2, aes(data_scale2$accelerator)) + geom_histogram(bins = 100)
```


```{r}
ggplot(data_scale2, aes(x=steering, y=-accelerator)) +
    geom_point(shape=1)      # Use hollow circles
```


```{r get-car-data}
  query <- 'SELECT * FROM public."FullCarData" WHERE idSession=$1;'
  session_car_data <- dbGetQuery(connection, query,c(session_id))
```


```{r}
summary(session_car_data)
```

```{r get-car-data_full}
  query <- 'SELECT * FROM public."FullCarData" JOIN public."WorldSpeed" USING ("time", idsession, speed) JOIN public."LapNumber1" USING ("time", idsession) WHERE idSession=$1;'
  session_car_data <- dbGetQuery(connection, query,c(392))
  #session_car_data <- head(session_car_data,6763)
```


```{r}
summary(session_car_data)
```


```{r}
session_car_data_sector1 <- subset(session_car_data, distance > 500 & distance <= 900)
summary(session_car_data_sector1)
```


```{r}
ggplot(session_car_data_sector1, aes(x=posx, y=posy, color=speed)) +
      geom_point(shape=16, size = 0.75)  + scale_x_continuous(limits = c(-750, 750)) + scale_y_continuous(limits = c(-40, 10))  + scale_color_gradient(low="blue", high="red")
ggsave("positionAndSpeedSector1.png", width = 7, height = 5)
```

```{r}
ggplot(session_car_data_sector1, aes(x=distance, y=speed ,color=idsession)) +
       geom_path(size=1.0)  + scale_color_gradient(low="white", high="blue")
ggsave("distanceSpeed.png", width = 7, height = 5)
```

```{r}
ggplot(session_car_data_sector1, aes(x=distance, y=brake)) + 
      geom_line(size=1.0)  + scale_color_gradient(low="white", high="blue")
ggsave("distanceBrake.png", width = 7, height = 5)
```

```{r}
ggplot(session_car_data_sector1, aes(x=distance, y=throttle)) + 
       geom_line()  + scale_color_gradient(low="white", high="blue")
ggsave("distanceThrottle.png", width = 7, height = 5)
```


```{r}
ggplot(session_car_data_sector1, aes(x=distance, y=steering)) + 
      geom_line()  + scale_color_gradient(low="white", high="blue")
ggsave("distanceSteering.png", width = 7, height = 5)
```

```{r}
ggplot(session_car_data_sector1, aes(x=speed, y=rpm)) + 
      geom_point(shape=1)  + scale_color_gradient(low="white", high="blue")
```


```{r}
session_car_data_filtered2 <- subset(session_car_data, distance < 10 )
ggplot(session_car_data_filtered2, aes(x=posx, y=posy, color=speed)) +
      geom_point(shape=1)  + scale_x_continuous(limits = c(-750, 750)) +  scale_y_continuous(limits = c(-40, 10)) + scale_color_gradient(low="white", high="blue")
```



```{r}
ggplot(tmp, aes(x=distance, y=speed)) +
      geom_point(shape=1)  + scale_color_gradient(low="white", high="blue")
```


```{r}
ggplot(session_car_data_sector1, aes( throttle)) +
      geom_density()
ggsave("ThrottleDensity.png", width = 7, height = 5)
```

```{r}
ggplot(session_car_data_sector1, aes( rpm)) +
      geom_density()
ggsave("RpmDensity.png", width = 7, height = 5)
```

```{r get-time}
  query <- 'SELECT * FROM public."FullCarData" JOIN public."WorldSpeed" USING ("time", idsession, speed) JOIN public."LapNumber1" USING ("time", idsession) WHERE idSession=$1;'
  session_car_data2 <- dbGetQuery(connection, query,c(392))
```

```{r}
summary(session_car_data2)
scds <- max(session_car_data2$currenttime,na.rm=TRUE)

seconds_to_period(scds)
```